EDA

### 2020-02-27 src/draft.Rmd
added plots

---
title: "EDA"
author: "Xuechun Lu, Yuting Wen, Peter Han"
date: "25/02/2020"
output: html_document
---

@@

## R Markdown
libraries
```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(here)
library(readxl)

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  numPlots = length(plots)
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }
 if (numPlots==1) {
    print(plots[[1]])
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

@@

1. data processing
```{r}
# all municipalities
municipality.list = c(
  "Burnaby", 
  "Coquitlam", 
  "Delta", 
  "Langley - City", 
  "Langley - Township",
  "Maple Ridge",
  "Maple Ridge Rural", 
  "North Vancouver - City",
  "North Vancouver - Dist",
  "Pitt Meadows", 
  "Port Coquitlam", 
  "Port Moody", 
  "Richmond", 
  "Surrey", 
  "Vancouver", 
  "White Rock", 
  "West Vancouver", 
  "Bowen Island", 
  "Anmore", 
  "Belcarra",
  "Lions Bay")

@@

3. pct_plots
pct change of mill rates for each tax class
```{r}
tax.list<-c("01","05","06")
pct_rate1 <- pct_final %>% 
  filter(Municipalities %in% municipality.list) %>%
  filter(TaxClassCode == "01") %>%
  ggplot(aes(x=Year, y=rate_pct, group=Municipalities, color=Municipalities)) +
    geom_line() + ggtitle("taxClass1 pct rate v.s year") + theme(legend.position = "none")

@@

tax_156 <- pct_final %>% filter(Municipalities == municipality.list[i]) %>% 
  filter(TaxClassCode %in% tax.list) %>% 
  ggplot(aes(x=Year, y=tax)) +
   geom_line() + theme(legend.position = "none") + ggtitle("tax amount")

multiplot(pct_rate1,pct_assess1,tax_156)
multiplot(pct_rate5,pct_assess5,tax_156)
multiplot(pct_rate6,pct_assess6,tax_156)
```
pct change of mill rate for each municipality
```{r}
# for each municipality
for (i in 1:21){
  plot<-pct_final %>% filter(Municipalities == municipality.list[i]) %>% 
  filter(TaxClassCode %in% tax.list) %>% 
  ggplot(aes(x=Year, y=rate_pct, group=TaxClassCode, color=TaxClassCode)) +
    geom_line() + ggtitle(municipality.list[i])
  print(plot)
}
```

>>>>

---
title: "EDA"
author: "Xuechun Lu, Yuting Wen, Peter Han"
date: "25/02/2020"
output:
  github_document
---

@@

## R Markdown
libraries
```{r, message=F, warning=F}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(here)
library(readxl)
```

```{r}
multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
  library(grid)
  # Make a list from the ... arguments and plotlist
  plots <- c(list(...), plotlist)
  numPlots = length(plots)
  # If layout is NULL, then use 'cols' to determine layout
  if (is.null(layout)) {
    # Make the panel
    # ncol: Number of columns of plots
    # nrow: Number of rows needed, calculated from # of cols
    layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                    ncol = cols, nrow = ceiling(numPlots/cols))
  }
 if (numPlots==1) {
    print(plots[[1]])
  } else {
    # Set up the page
    grid.newpage()
    pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
    # Make each plot, in the correct location
    for (i in 1:numPlots) {
      # Get the i,j matrix positions of the regions that contain this subplot
      matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
      print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                      layout.pos.col = matchidx$col))
    }
  }
}

@@

1. data processing
```{r, warning=F, message=F}
# all municipalities
municipality.list = c(
  "Burnaby", 
  "Coquitlam", 
  "Delta", 
  "Langley - City", 
  "Langley - Township",
  "Maple Ridge",
  "Maple Ridge Rural", 
  "North Vancouver - City",
  "North Vancouver - Dist",
  "Pitt Meadows", 
  "Port Coquitlam", 
  "Port Moody", 
  "Richmond", 
  "Surrey", 
  "Vancouver", 
  "White Rock", 
  "West Vancouver", 
  "Bowen Island", 
  "Anmore", 
  "Belcarra",
  "Lions Bay")

@@

3. pct_plots
pct change of mill rates for each tax class
```{r}
pct_rate1 <- pct_final %>% 
  filter(Municipalities %in% municipality.list) %>%
  filter(TaxClassCode == "01") %>%
  ggplot(aes(x=Year, y=rate_pct, group=Municipalities, color=Municipalities)) +
    geom_line() + ggtitle("taxClass1 pct rate v.s year") + theme(legend.position = "none")

@@

multiplot(pct_rate1,pct_assess1)
multiplot(pct_rate5,pct_assess5)
multiplot(pct_rate6,pct_assess6)
```
pct change of mill rate for each municipality
```{r}
# for each municipality
tax.list <- c("01","05","06")
for (i in 1:21){
  plot<-pct_final %>% filter(Municipalities == municipality.list[i]) %>% 
  filter(TaxClassCode %in% tax.list) %>% 
  ggplot(aes(x=Year, y=rate_pct, group=TaxClassCode, color=TaxClassCode)) +
    geom_line() + ggtitle(municipality.list[i])
  print(plot)
}
```
